|

### 2021-08-17 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd
edits: parameter name correction

\newpage
\pagenumbering{arabic}

# Theory

@@

```{=tex}
\begin{equation}
\begin{aligned}
  u_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 \alpha_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
\end{aligned}
\end{equation}
```
where $\zeta_k$ ($k = 0-8$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-8}$). Explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.

The sensitivity analysis revealed key simulation parameters. For the effects of $N_p$, the following simulation parameters were influential: the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\gamma$ diversity), the maximum value of interspecific competition coefficient ($\alpha_{max}$; influenced the effects on $\alpha$, $\beta$, and $\gamma$ diversity), dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal probability ($p_d$; influenced the effect on $\alpha$ diversity) (**Table S3**). For the effects of $P_b$, the following simulation parameters were influential: environmental variation at headwaters ($\sigma_h$; influenced the effect on $\gamma$ diversity), the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity) (**Table S4**).

Based on the results, we identified $\sigma_h$, $\sigma_l$, $\alpha_{max}$, $\theta$, and $p_d$ as key parameters. We changed the values of these parameters in the main analysis and examined the relationships between diversity metrics and ecosystem properties.

@@

  figure_cap[i] <- paste0("Theoretical predictions for longitudinal gradients of local species richness in branching networks. The longitudinal position of each habitat patch (x-axis) was expressed as the number of upstream habitat patches. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns and lines represent different dispersal scenarios (dispersal distance and probability). Left and right columns show long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$) scenarios repectively. Red and blue lines show low ($p_d = 0.01$) and high dispersal probabilities ($p_d = 0.10$). Other parameters are as follows: environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$; ecosystem size $N_{p} = 100$; ecosystem complexity $P_{b} = 0.5$.")
}

@@

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

@@

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competitive coefficients ($\\alpha_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

>>>>

```{=tex}
\newpage
\pagenumbering{arabic}
```
# Theory

@@

```{=tex}
\begin{equation}
\begin{aligned}
  u_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 b_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
\end{aligned}
\end{equation}
```
where $\zeta_k$ ($k = 0-8$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-8}$). Explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.

The sensitivity analysis revealed key simulation parameters. For the effects of $N_p$, the following simulation parameters were influential: the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\gamma$ diversity), the maximum value of interspecific competition coefficient ($b_{max}$; influenced the effects on $\alpha$, $\beta$, and $\gamma$ diversity), dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal probability ($p_d$; influenced the effect on $\alpha$ diversity) (**Table S3**). For the effects of $P_b$, the following simulation parameters were influential: environmental variation at headwaters ($\sigma_h$; influenced the effect on $\gamma$ diversity), the degree of local environmental noise ($\sigma_l$; influenced the effects on $\alpha$ and $\beta$ diversity), and dispersal distance ($\theta$; influenced the effects on $\alpha$ and $\beta$ diversity) (**Table S4**).

Based on the results, we identified $\sigma_h$, $\sigma_l$, $b_{max}$, $\theta$, and $p_d$ as key parameters. We changed the values of these parameters in the main analysis and examined the relationships between diversity metrics and ecosystem properties.

@@

  figure_cap[i] <- paste0("Theoretical predictions for longitudinal gradients of local species richness in branching networks. The longitudinal position of each habitat patch (x-axis) was expressed as the number of upstream habitat patches. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns and lines represent different dispersal scenarios (dispersal distance and probability). Left and right columns show long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$) scenarios repectively. Red and blue lines show low ($p_d = 0.01$) and high dispersal probabilities ($p_d = 0.10$). Other parameters are as follows: environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$; ecosystem size $N_{p} = 100$; ecosystem complexity $P_{b} = 0.5$.")
}

@@

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem size influences (the number of habitat patches) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}

@@

  figure_cap[i] <- paste0("Theoretical predictions for ecosystem complexity influences (branching probability) on $\\alpha$, $\\beta$, and $\\gamma$ diversity in branching networks. `r conditional_text[",i,"]` Lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Each panel represents different ecological scenarios under which metacommunity dynamics were simulated. Rows represent different competition strength. Competition coefficients ($b_{ij}$) were varied randomly from 0 to 1.5 (top, strong competition) or 0.75 (bottom, weak competition). Columns represent different dispersal scenarios. Two dispersal parameters were chosen to simulate scenarios with long-distance (the rate parameter of an exponential dispersal kernel $\\theta = 0.10$) and short-distance dispersal ($\\theta = 1.0$). Other parameters are as follows: dispersal probability $p_{d} = `r param$p_d[",i,"]`$; environmental variation at headwaters $\\sigma_{h} = `r param$sigma_h[",i,"]`$; local environmental noise $\\sigma_{l} = `r param$sigma_l[",i,"]`$.")
}
